### 2016-10-01 tasks_and_ideas.tex
Spell checks

\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this. \tsnote{Not sure if this requires new syntax and/or notions.  But basically this is what the Neidermayer et al.\ attacks exploit -- that medical records consist of multiple fields, and the record-linkage protocol produces a BF for each field.  (If you think of records as rows in a DB, there's a BF for each column.) One of the fields is the patient's surname, and the attack uses clever frequency analysis to recover surnames.}

@@

\item Break a Squid server!  I'm thinking about a privacy break here.  One could start by simulating the (very simple) Bloom filter that Squid implements, and eventually stand up an actual Squid proxy.  Perhaps populate the filter with a random sampling of URLs from the Alexa top 1000.  (How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermayer et al.\ to infer information about which URLs are cached.  Of course, there's a timing based attack, just pinging the Squid proxy with URLs.   But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses. \tsnote{Apparently Crosby and Wallach gives some attacks.} \tsnote{Gerbet et al. give some generic attacks that are interesting.  I wonder if Squid, because it uses MD5, admits faster ``pollution attacks'' on the filter, e.g. where the adversary finds URLs that would set far more bits to 1 than one would expect? (Yep, see Crosby and Wallach.)}

@@

\item Speaking of the Niedermayer et al. attacks, these exploit the fact that there are different bloom filters for different record identifiers (i.e. one for last name, one for first name, one for city, etc.).  They propose various way to render their attacks useless, or at least very inefficient.  Can we actually prove something about one or more of the proposed countermeasures?

>>>>

\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this. \tsnote{Not sure if this requires new syntax and/or notions.  But basically this is what the Niedermeyer et al.\ attacks exploit -- that medical records consist of multiple fields, and the record-linkage protocol produces a BF for each field.  (If you think of records as rows in a DB, there's a BF for each column.) One of the fields is the patient's surname, and the attack uses clever frequency analysis to recover surnames.}

@@

\item Break a Squid server!  I'm thinking about a privacy break here.  One could start by simulating the (very simple) Bloom filter that Squid implements, and eventually stand up an actual Squid proxy.  Perhaps populate the filter with a random sampling of URLs from the Alexa top 1000.  (How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermeyer et al.\ to infer information about which URLs are cached.  Of course, there's a timing based attack, just pinging the Squid proxy with URLs.   But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses. \tsnote{Apparently Crosby and Wallach gives some attacks.} \tsnote{Gerbet et al. give some generic attacks that are interesting.  I wonder if Squid, because it uses MD5, admits faster ``pollution attacks'' on the filter, e.g. where the adversary finds URLs that would set far more bits to 1 than one would expect? (Yep, see Crosby and Wallach.)}

@@

\item Speaking of the Niedermeyer et al. attacks, these exploit the fact that there are different bloom filters for different record identifiers (i.e. one for last name, one for first name, one for city, etc.).  They propose various way to render their attacks useless, or at least very inefficient.  Can we actually prove something about one or more of the proposed countermeasures?
